NFC and burnout in teachers - A replication and extension study

### 2022-02-24 Manuscript/Manuscript.tex
none of the decimal alignments worked and I'm mad

\cellcolor{gray!6}{1. MBI} & \cellcolor{gray!6}{\&nbsp; .90(.91)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
2. MBI EE & \&nbsp; .92*** & \&nbsp; .91(.92) &  &  &  &  &  &  &  &  &  &  & \\
\cellcolor{gray!6}{3. MBI DP} & \cellcolor{gray!6}{\&nbsp; .75***} & \cellcolor{gray!6}{\&nbsp; .54***} & \cellcolor{gray!6}{\&nbsp; .68(.69)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
4. MBI RPE & \&nbsp; .67*** & \&nbsp; .43*** & \&nbsp; .48*** & \&nbsp; .79(.79) &  &  &  &  &  &  &  &  & \\
\cellcolor{gray!6}{5. ERQ} & \cellcolor{gray!6}{-.06} & \cellcolor{gray!6}{-.06} & \cellcolor{gray!6}{\&nbsp; .04} & \cellcolor{gray!6}{-.10} & \cellcolor{gray!6}{\&nbsp; .73(.62)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\

@@

6. ERQ S & \&nbsp; .05 & -.00 & \&nbsp; .17* & \&nbsp; .08 & \&nbsp; .59*** & \&nbsp; .75(.79) &  &  &  &  &  &  & \\
\cellcolor{gray!6}{7. ERQ R} & \cellcolor{gray!6}{-.10} & \cellcolor{gray!6}{-.06} & \cellcolor{gray!6}{-.06} & \cellcolor{gray!6}{-.20**} & \cellcolor{gray!6}{\&nbsp; .71***} & \cellcolor{gray!6}{-.07} & \cellcolor{gray!6}{\&nbsp; .84(.84)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
8. SCS & -.34*** & -.28*** & -.37*** & -.19* & -.03 & -.12 & \&nbsp; .05 & \&nbsp; .85(.86) &  &  &  &  & \\
\cellcolor{gray!6}{9. NFC} & \cellcolor{gray!6}{-.25***} & \cellcolor{gray!6}{-.20**} & \cellcolor{gray!6}{-.22**} & \cellcolor{gray!6}{-.21**} & \cellcolor{gray!6}{-.01} & \cellcolor{gray!6}{-.18*} & \cellcolor{gray!6}{\&nbsp; .16*} & \cellcolor{gray!6}{\&nbsp; .22**} & \cellcolor{gray!6}{\&nbsp; .89(.89)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
10. DTH & \&nbsp; .67*** & \&nbsp; .72*** & \&nbsp; .35*** & \&nbsp; .36*** & \&nbsp; .03 & \&nbsp; .05 & -.01 & -.21** & -.15* & \&nbsp; .73(.73) &  &  & \\

@@

\cellcolor{gray!6}{11. DTL} & \cellcolor{gray!6}{\&nbsp; .44***} & \cellcolor{gray!6}{\&nbsp; .36***} & \cellcolor{gray!6}{\&nbsp; .38***} & \cellcolor{gray!6}{\&nbsp; .43***} & \cellcolor{gray!6}{\&nbsp; .01} & \cellcolor{gray!6}{\&nbsp; .16*} & \cellcolor{gray!6}{-.14} & \cellcolor{gray!6}{-.19*} & \cellcolor{gray!6}{-.16*} & \cellcolor{gray!6}{\&nbsp; .41***} & \cellcolor{gray!6}{\&nbsp; .73(.75)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
12. DRF & -.55*** & -.46*** & -.41*** & -.53*** & -.00 & -.10 & \&nbsp; .10 & \&nbsp; .18* & \&nbsp; .24** & -.42*** & -.56*** & \&nbsp; .77(.77) & \\
\cellcolor{gray!6}{13. COV} & \cellcolor{gray!6}{\&nbsp; .24**} & \cellcolor{gray!6}{\&nbsp; .32***} & \cellcolor{gray!6}{\&nbsp; .08} & \cellcolor{gray!6}{\&nbsp; .02} & \cellcolor{gray!6}{-.03} & \cellcolor{gray!6}{\&nbsp; .02} & \cellcolor{gray!6}{-.07} & \cellcolor{gray!6}{-.04} & \cellcolor{gray!6}{\&nbsp; .13} & \cellcolor{gray!6}{\&nbsp; .45***} & \cellcolor{gray!6}{\&nbsp; .10} & \cellcolor{gray!6}{-.13} & \cellcolor{gray!6}{\&nbsp; .77(.81)}\\

@@

\cellcolor{gray!6}{1. MBI} & \cellcolor{gray!6}{\&nbsp; .90(.91)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
2. MBI EE & \&nbsp; .92*** & \&nbsp; .91(.91) &  &  &  &  &  &  &  &  &  &  & \\
\cellcolor{gray!6}{3. MBI DP} & \cellcolor{gray!6}{\&nbsp; .74***} & \cellcolor{gray!6}{\&nbsp; .53***} & \cellcolor{gray!6}{\&nbsp; .68(.66)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
4. MBI RPE & \&nbsp; .66*** & \&nbsp; .42*** & \&nbsp; .47*** & \&nbsp; .79(.78) &  &  &  &  &  &  &  &  & \\
\cellcolor{gray!6}{5. ERQ} & \cellcolor{gray!6}{-.05} & \cellcolor{gray!6}{-.05} & \cellcolor{gray!6}{\&nbsp; .05} & \cellcolor{gray!6}{-.09} & \cellcolor{gray!6}{\&nbsp; .73(.62)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\

@@

6. ERQ S & \&nbsp; .05 & -.00 & \&nbsp; .17* & \&nbsp; .08 & \&nbsp; .59*** & \&nbsp; .75(.79) &  &  &  &  &  &  & \\
\cellcolor{gray!6}{7. ERQ R} & \cellcolor{gray!6}{-.09} & \cellcolor{gray!6}{-.05} & \cellcolor{gray!6}{-.05} & \cellcolor{gray!6}{-.19*} & \cellcolor{gray!6}{\&nbsp; .71***} & \cellcolor{gray!6}{-.07} & \cellcolor{gray!6}{\&nbsp; .84(.84)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
8. SCS & -.33*** & -.27*** & -.36*** & -.17* & -.04 & -.12 & \&nbsp; .04 & \&nbsp; .85(.85) &  &  &  &  & \\
\cellcolor{gray!6}{9. NFC} & \cellcolor{gray!6}{-.24**} & \cellcolor{gray!6}{-.18*} & \cellcolor{gray!6}{-.21**} & \cellcolor{gray!6}{-.20**} & \cellcolor{gray!6}{-.02} & \cellcolor{gray!6}{-.18*} & \cellcolor{gray!6}{\&nbsp; .15*} & \cellcolor{gray!6}{\&nbsp; .20**} & \cellcolor{gray!6}{\&nbsp; .89(.88)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
10. DTH & \&nbsp; .66*** & \&nbsp; .72*** & \&nbsp; .34*** & \&nbsp; .35*** & \&nbsp; .04 & \&nbsp; .05 & \&nbsp; .00 & -.19** & -.13 & \&nbsp; .73(.72) &  &  & \\

@@

\cellcolor{gray!6}{11. DTL} & \cellcolor{gray!6}{\&nbsp; .44***} & \cellcolor{gray!6}{\&nbsp; .35***} & \cellcolor{gray!6}{\&nbsp; .37***} & \cellcolor{gray!6}{\&nbsp; .42***} & \cellcolor{gray!6}{\&nbsp; .01} & \cellcolor{gray!6}{\&nbsp; .16*} & \cellcolor{gray!6}{-.13} & \cellcolor{gray!6}{-.18*} & \cellcolor{gray!6}{-.15*} & \cellcolor{gray!6}{\&nbsp; .40***} & \cellcolor{gray!6}{\&nbsp; .73(.76)} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
12. DRF & -.54*** & -.45*** & -.40*** & -.52*** & -.01 & -.10 & \&nbsp; .09 & \&nbsp; .16* & \&nbsp; .23** & -.41*** & -.55*** & \&nbsp; .77(.75) & \\
\cellcolor{gray!6}{13. COV} & \cellcolor{gray!6}{\&nbsp; .23**} & \cellcolor{gray!6}{\&nbsp; .32***} & \cellcolor{gray!6}{\&nbsp; .07} & \cellcolor{gray!6}{\&nbsp; .00} & \cellcolor{gray!6}{-.02} & \cellcolor{gray!6}{\&nbsp; .02} & \cellcolor{gray!6}{-.06} & \cellcolor{gray!6}{-.03} & \cellcolor{gray!6}{\&nbsp; .14} & \cellcolor{gray!6}{\&nbsp; .44***} & \cellcolor{gray!6}{\&nbsp; .08} & \cellcolor{gray!6}{-.12} & \cellcolor{gray!6}{\&nbsp; .77(.81)}\\

>>>>

\cellcolor{gray!6}{1. MBI} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
2. MBI EE & .92*** &  &  &  &  &  &  &  &  &  &  &  & \\
\cellcolor{gray!6}{3. MBI DP} & \cellcolor{gray!6}{.75***} & \cellcolor{gray!6}{.54***} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
4. MBI RPE & .67*** & .43*** & .48*** &  &  &  &  &  &  &  &  &  & \\
\cellcolor{gray!6}{5. ERQ} & \cellcolor{gray!6}{-.06} & \cellcolor{gray!6}{-.06} & \cellcolor{gray!6}{.04} & \cellcolor{gray!6}{-.10} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\

@@

6. ERQ S & .05 & -.00 & .17* & .08 & .59*** &  &  &  &  &  &  &  & \\
\cellcolor{gray!6}{7. ERQ R} & \cellcolor{gray!6}{-.10} & \cellcolor{gray!6}{-.06} & \cellcolor{gray!6}{-.06} & \cellcolor{gray!6}{-.20**} & \cellcolor{gray!6}{.71***} & \cellcolor{gray!6}{-.07} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
8. SCS & -.34*** & -.28*** & -.37*** & -.19* & -.03 & -.12 & .05 &  &  &  &  &  & \\
\cellcolor{gray!6}{9. NFC} & \cellcolor{gray!6}{-.25***} & \cellcolor{gray!6}{-.20**} & \cellcolor{gray!6}{-.22**} & \cellcolor{gray!6}{-.21**} & \cellcolor{gray!6}{-.01} & \cellcolor{gray!6}{-.18*} & \cellcolor{gray!6}{.16*} & \cellcolor{gray!6}{.22**} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
10. DTH & .67*** & .72*** & .35*** & .36*** & .03 & .05 & -.01 & -.21** & -.15* &  &  &  & \\

@@

\cellcolor{gray!6}{11. DTL} & \cellcolor{gray!6}{.44***} & \cellcolor{gray!6}{.36***} & \cellcolor{gray!6}{.38***} & \cellcolor{gray!6}{.43***} & \cellcolor{gray!6}{.01} & \cellcolor{gray!6}{.16*} & \cellcolor{gray!6}{-.14} & \cellcolor{gray!6}{-.19*} & \cellcolor{gray!6}{-.16*} & \cellcolor{gray!6}{.41***} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
12. DRF & -.55*** & -.46*** & -.41*** & -.53*** & -.00 & -.10 & .10 & .18* & .24** & -.42*** & -.56*** &  & \\
\cellcolor{gray!6}{13. COV} & \cellcolor{gray!6}{.24**} & \cellcolor{gray!6}{.32***} & \cellcolor{gray!6}{.08} & \cellcolor{gray!6}{.02} & \cellcolor{gray!6}{-.03} & \cellcolor{gray!6}{.02} & \cellcolor{gray!6}{-.07} & \cellcolor{gray!6}{-.04} & \cellcolor{gray!6}{.13} & \cellcolor{gray!6}{.45***} & \cellcolor{gray!6}{.10} & \cellcolor{gray!6}{-.13} & \cellcolor{gray!6}{}\\

@@

\cellcolor{gray!6}{1. MBI} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
2. MBI EE & .92*** &  &  &  &  &  &  &  &  &  &  &  & \\
\cellcolor{gray!6}{3. MBI DP} & \cellcolor{gray!6}{.74***} & \cellcolor{gray!6}{.53***} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
4. MBI RPE & .66*** & .42*** & .47*** &  &  &  &  &  &  &  &  &  & \\
\cellcolor{gray!6}{5. ERQ} & \cellcolor{gray!6}{-.05} & \cellcolor{gray!6}{-.05} & \cellcolor{gray!6}{.05} & \cellcolor{gray!6}{-.09} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\

@@

6. ERQ S & .05 & -.00 & .17* & .08 & .59*** &  &  &  &  &  &  &  & \\
\cellcolor{gray!6}{7. ERQ R} & \cellcolor{gray!6}{-.09} & \cellcolor{gray!6}{-.05} & \cellcolor{gray!6}{-.05} & \cellcolor{gray!6}{-.19*} & \cellcolor{gray!6}{.71***} & \cellcolor{gray!6}{-.07} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
8. SCS & -.33*** & -.27*** & -.36*** & -.17* & -.04 & -.12 & .04 &  &  &  &  &  & \\
\cellcolor{gray!6}{9. NFC} & \cellcolor{gray!6}{-.24**} & \cellcolor{gray!6}{-.18*} & \cellcolor{gray!6}{-.21**} & \cellcolor{gray!6}{-.20**} & \cellcolor{gray!6}{-.02} & \cellcolor{gray!6}{-.18*} & \cellcolor{gray!6}{.15*} & \cellcolor{gray!6}{.20**} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
10. DTH & .66*** & .72*** & .34*** & .35*** & .04 & .05 & .00 & -.19** & -.13 &  &  &  & \\

@@

\cellcolor{gray!6}{11. DTL} & \cellcolor{gray!6}{.44***} & \cellcolor{gray!6}{.35***} & \cellcolor{gray!6}{.37***} & \cellcolor{gray!6}{.42***} & \cellcolor{gray!6}{.01} & \cellcolor{gray!6}{.16*} & \cellcolor{gray!6}{-.13} & \cellcolor{gray!6}{-.18*} & \cellcolor{gray!6}{-.15*} & \cellcolor{gray!6}{.40***} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
12. DRF & -.54*** & -.45*** & -.40*** & -.52*** & -.01 & -.10 & .09 & .16* & .23** & -.41*** & -.55*** &  & \\
\cellcolor{gray!6}{13. COV} & \cellcolor{gray!6}{.23**} & \cellcolor{gray!6}{.32***} & \cellcolor{gray!6}{.07} & \cellcolor{gray!6}{.00} & \cellcolor{gray!6}{-.02} & \cellcolor{gray!6}{.02} & \cellcolor{gray!6}{-.06} & \cellcolor{gray!6}{-.03} & \cellcolor{gray!6}{.14} & \cellcolor{gray!6}{.44***} & \cellcolor{gray!6}{.08} & \cellcolor{gray!6}{-.12} & \cellcolor{gray!6}{}\\
